Article Name

### 2022-09-27 elsevier/manuscript.Rmd
add table with LaTeX math symbols

````markdown
`r ''````{r}
data %>% 
          group_by(supp) %>%
          summarise(median = median(len),
                    mean = mean(len)) %>% 
	kable("simple",
	      booktabs = T,
	      col.names = c("Supplement type", 
	      	    	"Median",
	      	    	"Mean"), 
	      align = "cll",
	      caption = "\\label{tab:cooltable}Mean and Median")
```
````

```{r}
data %>% 
          group_by(supp) %>%
          summarise(median = median(len),
                    mean = mean(len)) %>% 
	kable("simple",
	      booktabs = T,
	      col.names = c("Supplement type", 
	      	    	"Median",
	      	    	"Mean"), 
	      align = "cll",
	      caption = "\\label{tab:cooltable}Mean and Median")
```

>>>>

````markdown
`r ''````{r table1}
data %>% 
          group_by(supp) %>%
          summarise(median = median(len),
                    mean = mean(len)) %>% 
	kable("latex",
	      booktabs = T,
	      col.names = c("Supplement type", 
	      	    	"Median",
	      	    	"Mean"), 
	      align = "cll",
	      caption = "\\label{tab:cooltable}Mean and Median")
```
````

```{r}
data %>% 
          group_by(supp) %>%
          summarise(median = median(len),
                    mean = mean(len)) %>% 
	kable("latex",
	      booktabs = T,
	      col.names = c("Supplement type", 
	      	    	"Median",
	      	    	"Mean"), 
	      align = "cll",
	      caption = "\\label{tab:cooltable}Mean and Median")
```

````markdown
`r ''````{r table2}
para = c("Intercept ($\\beta_0$)",
         "Parameter 1 ($\\beta_1$)",
         "Parameter 2 ($\\beta_2$)",
         "Hurdle probability ($\\theta$)")

tab <- data.frame(
	Parameter = para,
	Estimate = c(1.6, 1.2, 6.2, 0.5),
	Error = c(0.41, 0.02, 0.09, 0.07),
	CI = c("[0.698, 2.477]",
	       "[1.123, 1.235]",
	       "[6.051, 6.423]",
	       "[0.353, 0.644]"),
	Rhat = c(rep("1.00", 4)))

kable(tab,
      "latex",
      align = "lcccc",
      booktabs = TRUE,
      escape = FALSE,
      caption = "\\label{tab:mathtable}A table with LaTeX Math symbols")
```
````

```{r}
para = c("Intercept ($\\beta_0$)",
         "Parameter 1 ($\\beta_1$)",
         "Parameter 2 ($\\beta_2$)",
         "Hurdle probability ($\\theta$)")

tab <- data.frame(
	Parameter = para,
	Estimate = c(1.6, 1.2, 6.2, 0.5),
	Error = c(0.41, 0.02, 0.09, 0.07),
	CI = c("[0.698, 2.477]",
	       "[1.123, 1.235]",
	       "[6.051, 6.423]",
	       "[0.353, 0.644]"),
	Rhat = c(rep("1.00", 4)))

kable(tab,
      "latex",
      align = "lcccc",
      booktabs = TRUE,
      escape = FALSE,
      caption = "\\label{tab:mathtable}A table with LaTeX Math symbols")
```

### 2022-09-27 elsevier/manuscript.tex
add table with LaTeX math symbols

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{```\{r\}}
\NormalTok{data %>% }
\BaseNTok{          group_by(supp) %>%}
\BaseNTok{          summarise(median = median(len),}
\BaseNTok{                    mean = mean(len)) %>% }
\BaseNTok{    kable("simple",}
\BaseNTok{          booktabs = T,}
\BaseNTok{          col.names = c("Supplement type", }
\BaseNTok{                    "Median",}
\BaseNTok{                    "Mean"), }
\BaseNTok{          align = "cll",}
\BaseNTok{          caption = "\textbackslash{}\textbackslash{}label\{tab:cooltable\}Mean and Median")}
\NormalTok{```}
\end{Highlighting}
\end{Shaded}

\begin{longtable}[]{@{}cll@{}}
\caption{\label{tab:unnamed-chunk-2}\label{tab:cooltable}Mean and
Median}\tabularnewline
\toprule
Supplement type & Median & Mean\tabularnewline
\midrule
\endfirsthead
\toprule
Supplement type & Median & Mean\tabularnewline
\midrule
\endhead
OJ & 22.7 & 20.66333\tabularnewline
VC & 16.5 & 16.96333\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}cll@{}}
\caption{\label{tab:unnamed-chunk-11}\label{tab:stable}This table
again}\tabularnewline
\toprule
Supplement type & Median & Mean\tabularnewline
\midrule
\endfirsthead
\toprule
Supplement type & Median & Mean\tabularnewline
\midrule
\endhead
OJ & 22.7 & 20.663\tabularnewline
VC & 16.5 & 16.963\tabularnewline
\bottomrule
\end{longtable}

>>>>

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{```\{r table1\}}
\NormalTok{data %>% }
\BaseNTok{          group_by(supp) %>%}
\BaseNTok{          summarise(median = median(len),}
\BaseNTok{                    mean = mean(len)) %>% }
\BaseNTok{    kable("latex",}
\BaseNTok{          booktabs = T,}
\BaseNTok{          col.names = c("Supplement type", }
\BaseNTok{                    "Median",}
\BaseNTok{                    "Mean"), }
\BaseNTok{          align = "cll",}
\BaseNTok{          caption = "\textbackslash{}\textbackslash{}label\{tab:cooltable\}Mean and Median")}
\NormalTok{```}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:unnamed-chunk-2}\label{tab:cooltable}Mean and Median}
\centering
\begin{tabular}[t]{cll}
\toprule
Supplement type & Median & Mean\\
\midrule
OJ & 22.7 & 20.66333\\
VC & 16.5 & 16.96333\\
\bottomrule
\end{tabular}
\end{table}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{```\{r table2\}}
\NormalTok{para = c("Intercept ($\textbackslash{}\textbackslash{}beta_0$)",}
\BaseNTok{         "Parameter 1 ($\textbackslash{}\textbackslash{}beta_1$)",}
\BaseNTok{         "Parameter 2 ($\textbackslash{}\textbackslash{}beta_2$)",}
\BaseNTok{         "Hurdle probability ($\textbackslash{}\textbackslash{}theta$)")}

\NormalTok{tab <- data.frame(}
\BaseNTok{    Parameter = para,}
\BaseNTok{    Estimate = c(1.6, 1.2, 6.2, 0.5),}
\BaseNTok{    Error = c(0.41, 0.02, 0.09, 0.07),}
\BaseNTok{    CI = c("[0.698, 2.477]",}
\BaseNTok{           "[1.123, 1.235]",}
\BaseNTok{           "[6.051, 6.423]",}
\BaseNTok{           "[0.353, 0.644]"),}
\BaseNTok{    Rhat = c(rep("1.00", 4)))}

\NormalTok{kable(tab,}
\BaseNTok{      "latex",}
\BaseNTok{      align = "lcccc",}
\BaseNTok{      booktabs = TRUE,}
\BaseNTok{      escape = FALSE,}
\BaseNTok{      caption = "\textbackslash{}\textbackslash{}label\{tab:mathtable\}A table with LaTeX Math symbols")}
\NormalTok{```}
\end{Highlighting}
\end{Shaded}

\begin{table}

\caption{\label{tab:unnamed-chunk-3}\label{tab:mathtable}A table with LaTeX Math symbols}
\centering
\begin{tabular}[t]{lcccc}
\toprule
Parameter & Estimate & Error & CI & Rhat\\
\midrule
Intercept ($\beta_0$) & 1.6 & 0.41 & {}[0.698, 2.477] & 1.00\\
Parameter 1 ($\beta_1$) & 1.2 & 0.02 & {}[1.123, 1.235] & 1.00\\
Parameter 2 ($\beta_2$) & 6.2 & 0.09 & {}[6.051, 6.423] & 1.00\\
Hurdle probability ($\theta$) & 0.5 & 0.07 & {}[0.353, 0.644] & 1.00\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{longtable}[]{@{}cll@{}}
\caption{\label{tab:unnamed-chunk-12}\label{tab:stable}This table
again}\tabularnewline
\toprule
Supplement type & Median & Mean\tabularnewline
\midrule
\endfirsthead
\toprule
Supplement type & Median & Mean\tabularnewline
\midrule
\endhead
OJ & 22.7 & 20.663\tabularnewline
VC & 16.5 & 16.963\tabularnewline
\bottomrule
\end{longtable}
